Measuring Individual Partisan Harm in Redistricting

### 2021-09-11 paper/paper.Rmd
remove question
sims + updates

```{r nj-vars, fig.cap="Various measures for an ensemble of New Jersey districting plans.", fig.width=6.5, fig.height=6.5}
#include_graphics(here("out/nj_vars.pdf"))
```

>>>>

Figure \ref{nj-maps} shows the baseline Democratic vote share by precinct, along with two hypothetical gerrymanders of the state, which were generated using the short-burst optimization approach of @cannon2020.
